\sysfull

### 2017-08-11 paper/evaluation.tex
combined tables

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|}
		\hline
		Application & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
		\hline\hline
		{bc} & 351 & 588 \\ %59\%
		{cem} & 388 & 721 \\ %53\%
		{cuckoo} & 483 & 762 \\ %63\%
		{rsa} & 887 & 1233 \\ %71\%
		{ar} & 483 & 762 \\ %63\%
		{dft} & {} & {} \\ %Two resolutions: 4 and 8 Bytes
		{dd} & {} & {} \\ %Data decompression size: 100 bytes
		{sort} & {} & {} \\
		\hline
	\end{tabular}
\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
\label{table:benchmark_list}
\end{table}

@@

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		{} & \multicolumn{2}{l|}{{PVAR size (Byte)}} & \multicolumn{2}{c|}{{No. tasks}} & \multicolumn{2}{c|}{{No. paging code}} \\
		\hline
		Nickname & Hand & Comp. & Hand & Comp. & Hand & Comp. \\
		\hline\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 \\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 \\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 \\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 \\
		ar & 166 & 218 & 11 & 6 & 112 & 333 \\
		sort & 104 & 104 & 4 & 2 & 70 & 23 \\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for Huffman in Table 5 and 6 is missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls\todo{calls or code? what is paging call?}{Kiwan} in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%\todo{except for cc and ar---why?}{Kiwan}. The result indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the DFT application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compile_time}. We used a {\em date}\todo{date or time?}{Kiwan} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		bc & cem & cuckoo & rsa & ar & sort \\
		\hline\hline
		3 & 2 & 6 & 86 & 34 & < 1 \\
		\hline
	\end{tabular}
	\caption{\sys compile time per application (seconds).}
\label{table:compile_time}
\end{table}

%\subsubsection{Task Coalescing Performance}
%\label{sec:results_coalescing}

>>>>

%\begin{table}[t]
%	\centering
%	\footnotesize
%	\begin{tabular}{|c|c|c|}
%		\hline
%		Application & SLOC (\sys) & SLOC (Chain~\cite{chain})\\
%		\hline\hline
%		{bc} & 351 & 588 \\ %59\%
%		{cem} & 388 & 721 \\ %53\%
%		{cuckoo} & 483 & 762 \\ %63\%
%		{rsa} & 887 & 1233 \\ %71\%
%		{ar} & 483 & 762 \\ %63\%
%		{dft} & {} & {} \\ %Two resolutions: 4 and 8 Bytes
%		{dd} & {} & {} \\ %Data decompression size: 100 bytes
%		{sort} & {} & {} \\
%		\hline
%	\end{tabular}
%\caption{List of benchmark programs used in \sys evaluation; SLOC: source lines of code.}
%\label{table:benchmark_list}
%\end{table}

@@

\begin{table}[t]
	\centering
	\footnotesize
        \renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{l|cc|cc|cc|cc|c}
		\hline
		{} & \multicolumn{2}{l|}{{\bf Prot. bytes}} & \multicolumn{2}{c|}{{\bf \# Tasks}} & \multicolumn{2}{c|}{{\bf \# Prot. acc.}} & \multicolumn{2}{c|}{\bf SLOC} & {\bf Comp.} \\
		App & Man. & Comp. & Man. & Comp. & Man. & Comp. & \multicolumn{1}{l}{\sys} & \multicolumn{1}{r|}{Chain~\cite{chain}} & {\bf time} \\
		\hline
		bc & 22 & 22 & 10 & 15 & 81 & 93 & 351 &588 & 3\\
		cem & 3492 & 3242 & 12 & 9 & 92 & 123 & 388 &721 & 2\\
		cuckoo & 282 & 288 & 15 & 6 & 90 & 76 & 483 &762 & 6\\
		rsa & 332 & 250 & 20 & 27 & 130 & 296 & 887 &1233 & 86\\
		ar & 166 & 218 & 11 & 6 & 112 & 333 & 483 &762 & 34\\
		sort & 104 & 104 & 4 & 2 & 70 & 23 & & & $<$1\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).\todo{Data for dd, dft, sort missing}{Kiwan}}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of the \sys compiler Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls\todo{calls or code? what is paging call?}{Kiwan} in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The results indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, the \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer aliasing. Thus, it results in the \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provided in Section~\ref{sec:result_compiler_time}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise the compiler can be used to simplify the programmability.

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile the DFT application since LLVM inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3}, \texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not provided by the LLVM MSP430 back-end.}. We compiled the apps on a 4-core virtual machine with 1\,GB memory with Arch Linux, running on Intel Core i5-6200U (2.30\,GHz) processor. The result are given in Table~\ref{table:compiler_result}. We used the {\tt time} linux command to measure the rough time. Most of the compile time was due to pointer aliasing, when calculating possible live ranges of variables. Apps such as RSA whose code size is large and uses a lot of variables, need longer compilation time due to a larger search space for pointer aliasing.

%\begin{table}[t]
%	\centering
%	\footnotesize
%	\begin{tabular}{|c|c|c|c|c|c|}
%		\hline
%		bc & cem & cuckoo & rsa & ar & sort \\
%		\hline\hline
%		3 & 2 & 6 & 86 & 34 & < 1 \\
%		\hline
%	\end{tabular}
%	\caption{\sys compile time per application (seconds).}
%\label{table:compile_time}
%\end{table}
%
%\subsubsection{Task Coalescing Performance}
%\label{sec:results_coalescing}
